Convective heat transport in stratified atmospheres at low and high Mach number

### 2017-07-26 tex/nusselt_paper.tex
rough broad changes to PRFluid format

%\documentclass[iop]{emulateapj}
\documentclass[aps, prl, twocolumn, nofootinbib, groupedaddress, amsfonts, amssymb, amsmath]{revtex4-1}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{natbib}
%\usepackage[colorlinks=True, linkcolor=blue, citecolor=blue]{hyperref}
%\usepackage[all]{hypcap}

@@

%%%%% Body of the paper
\section{Introduction}
\refstepcounter{section}
\label{sec:intro}
Convection transports energy in stellar and planetary atmospheres
where flows are compressible and
feel the atmospheric stratification.  This stratification 
is significant in regions such as
the convective envelope of the Sun, which spans 14 density scale heights.
In the bulk of these systems, particularly in the deep interior,
flows are at very low Mach number (Ma).  Unfortunately,
numerical constraints have restricted most studies of 
compressible convection to high Ma.
These prior studies \cite{graham1975, chan&all1982,
hurlburt&all1984, cattaneo&all1990, brummell&all1996,
brandenburg&all2005} have provided insight into the nature of
convection in the low temperature,
high Ma region near the Sun's surface. Few fundamental
properties of low Ma compressible convection, such as the scaling of
convective heat transport, are known.

@@

In this letter we study the behavior of convective heat transport, 
quantified by the Nusselt number (Nu), in plane-parallel, 
two- and three-dimensional, polytropically stratified atmospheres.  
We vary $\epsilon$ and Ra while holding Pr, aspect ratio, boundary conditions,
and initial atmospheric stratification
constant.  We also examine the behavior of flow properties, as quantified by Ma and Re.
We find here that the scaling of Nu in stratified, compressible convection 
is similar to that in \RB convection,
and that this scaling is not appreciably changed by the magnitude of the superadiabaticity.

\section{Experiment} 
\refstepcounter{section}
\label{sec:experiment}
We examine a monatomic ideal gas with an adiabatic index of
$\gamma = 5/3$ whose equation of state is $P = R\rho T$. This is consistent with the approach used in earlier work 
\cite{graham1975, chan&all1982, brandenburg&all2005,
hurlburt&all1984, cattaneo&all1990, cattaneo&all1991, brummell&all1996} 
and is the simplest stratified extension of RBC.
The atmospheres studied are initially polytropically stratified,
\begin{equation}
\begin{split}
\rho_0(z) &= \rho_{t}(1 + L_z - z)^m, \\
T_0(z)    &= T_{t}(1 + L_z - z),
\label{eqn:polytrope}
\end{split}
\end{equation}
where $m$ is the polytropic index and $L_z$ is the depth of the atmosphere.
The polytropic
index is set by the superadiabatic excess, $\epsilon = m_{ad} - m$, where
$m_{ad} = (\gamma - 1)^{-1}$ is the adiabatic value of $m$.
The height coordinate, $z$, increases upwards in the range $[0, L_z]$.
Subscript 0 indicates initial conditions and subscript $t$ indicates values
at $z = L_z$.   Stratified atmospheres have a fourth non-dimensional parameter,
the number of density scale heights, $n_{\rho} = \ln\left[\rho_0(z=0)/\rho_t\right]$.  We
specify the depth of the atmosphere, $L_z = e^{n_{\rho}/m} - 1$, by choosing
the initial value of $n_{\rho}$.
Throughout this letter we set $n_{\rho} = 3$.    Satisfying hydrostatic
equilibrium sets the value of gravity, $g = RT_t (m + 1)$, which is
constant with depth.  We study atmospheres with aspect
ratios of 4 where both the $x$ and $y$ coordinates have the range $[0, 4L_z]$.
In our 2D cases, we only consider $x$ and $z$.

These domains are nondimensionalized by setting
$R = T_t = \rho_t = 1$ at $z = L_z$.
By this choice, the non-dimensional
length scale is the inverse temperature gradient scale and the 
timescale is the isothermal sound crossing time, 
$\tau_I$, of this unit length.
Meaningful convective dynamics occur on 
timescales of the atmospheric buoyancy time,
$t_b = \tau_I \sqrt{L_z/g\epsilon}$.

At fixed $n_\rho$, convective dynamics are 
controlled by $\epsilon$ as well as the atmospheric diffusivities.
At a fixed value of
$\epsilon$, the diffusivities are set by the
Rayleigh number (Ra) and the Prandtl number (Pr),
\begin{equation}
\text{Ra}_{t} = \frac{g L_z^3 (\Delta S_0 / c_P)}{\nu_t\chi_t},
\qquad
\text{Pr} = \frac{\nu}{\chi},
\end{equation}
where $\Delta S_0 = \epsilon\ln (1 + L_z) = \epsilon n_\rho / m$ 
is the initial entropy difference across the domain,
$c_P = \gamma/(\gamma-1)$ is the specific heat at
constant pressure, $\nu$ is the thermal diffusivity, 
and $\chi$ is the kinematic viscosity.
Throughout this work we specify
that Pr $= 1$ and is depth invariant.
The initial thermal
conductivity, $\kappa_0 = \chi \rho_0$, is
constant with depth, such that (\ref{eqn:polytrope}) is in
thermal equilibrium ($\grad\cdot[\kappa_0\grad T_0] = 0$).
By these
choices, $\nu(z) \equiv \chi(z) \equiv \chi_t / \rho_0$.
This formulation 
sets Ra at the bottom of the domain greater than
Ra$_t$ by a factor of $e^{2n_\rho}$. Henceforth
when we specify Ra we are referring to Ra$_t$.  
The full values of $\kappa = \rho\chi$ and 
$\mu = \rho\nu$ (the dynamic viscosity) change as the density 
profile evolves.  
The diffusivities scale as
$\chi_t, \nu_t \propto \sqrt{g L_z^3 \epsilon / \text{Ra}_t}$.
Defining the thermal diffusion timescale as $t_\chi \equiv L_z^2 / \chi$, the
ratio of $t_\chi$ to the buoyancy time is
\begin{equation}
\frac{t_\chi}{t_b} = \left(\frac{c_P}{n_\rho}\right)^{1/2}\text{Ra}_t^{1/2}
\left(m_{ad} - \epsilon\right)^{1/2}.
\label{eqn:timescales}
\end{equation}
We carry out two experiments in this letter. In the first,
we fix $\epsilon$ and increase Ra, thus increasing the ratio in
(\ref{eqn:timescales}). In the second, we fix Ra and vary $\epsilon$,
scaling the buoyancy time $t_b$ as $\epsilon^{-1/2}$
relative to the speed of sound; we see this reflected in the evolved Mach
number scaling (Fig. \ref{fig:ma_v_eps}). The ratio in (\ref{eqn:timescales}) is
independent of $\epsilon$ when $\epsilon \ll m_{ad}$.

The Fully Compressible Navier-Stokes equations,
\begin{align}
&\begin{aligned}
&\frac{\partial \ln\rho}{\partial t} + \grad\cdot\bm{u} 
    = -\bm{u}\cdot\grad\ln\rho,
	\label{eqn:continuity_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{\partial\bm{u}}{\partial t} + \grad T - 
&\nu\grad\cdot\lilstressT - \lilstressT\cdot\grad\nu = \\
&-\bm{u}\cdot\grad\bm{u} - T\grad\ln\rho + \bm{g} + 
\nu\lilstressT\cdot\grad\ln\rho,
\label{eqn:momentum_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{\partial T}{\partial t} -\frac{1}{c_V}\left(\right.\chi&\left.
    \grad^2 T + \grad T\cdot\grad\chi\right) = \\
	&-\bm{u}\cdot\grad T - (\gamma-1)T\grad\cdot{\bm{u}} \\
	&+ \frac{1}{c_V}\left(\chi\grad T \cdot\grad\ln\rho +
	\nu\left[\lilstressT\cdot\nabla\right]\cdot\bm{u}\right), 
	\label{eqn:energy_eqn}
\end{aligned}
\end{align}
are evolved with the viscous stress tensor given by
\begin{equation}
\sigma_{ij} \equiv \left(\frac{\partial u_i}{\partial x_j} + 
\frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\grad\cdot\bm{u}\right).
	\label{eqn:stress_tensor}
\end{equation}
Taking an inner product of
(\ref{eqn:momentum_eqn}) with $\rho\bm{u}$ and adding it to 
$\rho c_V\times$(\ref{eqn:energy_eqn}) reveals the full energy equation,
\begin{equation}
\frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{cond}}} = 0,
	\label{eqn:energy_eqn_full}
\end{equation}
where
$
\bm{F}_{\text{conv}} \equiv \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}}
$
is the convective flux and $\bm{F}_{\text{cond}} = -\kappa \grad T$
is the conductive flux.
The individual contributions to $\bm{F}_{\text{conv}}$ are the enthalpy flux, 
$\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$;
the kinetic energy flux, 
$\bm{F}_{\text{KE}} \equiv \rho|\bm{u}|^2\bm{u}/2$;
the potential energy flux,
$\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ (with $\phi \equiv -gz$);
and the viscous flux, 
$\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$.
Understanding how each of these fluxes interact  
is crucial in characterizing convective heat transport.

@@

\section{Results \& Discussion}
\refstepcounter{section}
\label{sec:results}

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/ma_v_Ra.png}
\caption{The mean adiabatic Mach number of long-time-averaged profiles
is shown.  Error bars show the full range of Ma over the depth of the
atmosphere.
(a) Ma, at various values of Ra, 
is plotted as a function of $\epsilon$.
(b) Ma, at various values of $\epsilon$, 
is plotted as a function of Ra/Ra$_{\text{crit}}$.
Larger symbols with white dots designate 3D runs.
\label{fig:ma_v_eps} }
\end{figure}

@@

@@

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
\caption{Characteristic entropy fluctuations in evolved 2D flows roughly
140$t_b$ after the start of simulations. 
The time- and horizontally-averaged profile is removed in all cases.  
(a) A low Ma flow at moderate Ra. (b) A high Ma flow at the same Ra as in (a).
(c) A high Ma flow at high Ra.
Shock systems can be seen in the upper atmosphere of the high Ma flows,
for example at $(x, z) \sim (70, 15-19)$ in (b) and $(x, z) \sim 
(65, 17-19)$ in (c).
\label{fig:entropy_snapshots} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/re_and_nu_v_Ra.png}
\caption{
Flow properties at high and low $\epsilon$. 
(a) Nu vs. Ra/Ra$_{\text{crit}}$.
Errors bars indicate the variance of Nu with depth;
large error bars indicate a poorly converged solution.
(b) Re vs. Ra/Ra$_{\text{crit}}$.
Re is measured at the midplane of the atmosphere.
Larger symbols with white dots designate 3D runs.
 \label{fig:re_and_nu_v_ra}
}
\end{figure}

@@

The variation of Nu with Ra is shown in 
Fig. \ref{fig:re_and_nu_v_ra}a.  We find that the Nu depends primarily
on Ra, not on $\epsilon$, except where dynamical regimes change.
In 2D and at low to moderate Ra, 
Nu $\appropto$ Ra$^{1/3}$ regardless of $\epsilon$,
reminiscent of scaling laws in \RB boundary layer theory 
\cite{grossman&lohse2000, ahlers&all2009, king&all2012}.
As the flow becomes supersonic,  Nu $\appropto$ Ra$^{1/5}$.
%2D runs at $\text{Ra }\gtrsim 10^3$Ra$_{\text{crit}}$
%and $\epsilon = 10^{-4}$ exhibit windy convective states.
%In these runs, the system is in flux equilibrium only when
%time averaged over roll states and windy states.
%A long time average
%over both of these states produces a flat flux profile which
%can be sensibly analyzed, but the presence of these time-dependent states
%makes it difficult to equilibrate these higher Ra cases.
It is also important to note that, in 2D,
the value of Nu is heavily dependent upon the specific thermodynamic
structures of the solution, and slight changes in
Ra can result in a simulation converging to one solution or another. 
Select simulations were run at higher aspect ratios (8 and 16), and similar flow
morphologies were obtained, suggesting that these states are not highly
sensitive to aspect ratio.
In our limited 3D runs, it appears that Nu $\appropto$ Ra$^{2/7}$, a classic scaling law
seen in RBC \cite{johnston&doering2009}.

@@

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/density_v_ra.png}
\caption{\label{fig:nrho_v_ra} 
Solid symbols show the density contrast measured
in density scale heights between the upper and lower boundary, 
$n_\rho = \ln[\rho(z=0)/\rho(z=L_z)]$.
Empty symbols show 
$n_\rho = \ln[\text{max}(\rho)/\text{min}(\rho)]$. 
At low $\epsilon$ the evolved
$n_{\rho}$ is close to the initial conditions of $n_\rho = 3$.  
At high $\epsilon$,
the density stratification decreases.  Once the mean 
Ma approaches 1 (at Ra/Ra$_{\text{crit}} \approx \{10^2, 10^3\}$ for $\epsilon = \{1, 0.5\}$
as in Fig. \ref{fig:ma_v_eps}b), density inversions form within the thermal
boundary layers. Larger symbols represent 3D runs.}
\end{figure}

@@

%Discussion

In summary, we have found that the evolved flow properties of stratified,
compressible convection scale in a manner reminiscent of RBC.
We argue that polytropically stratified atmospheres are the natural
extension of the RBC problem with an additional control parameter, $\epsilon$,
whose primary role is to set the Ma of the flows.  We show that other properties
of the evolved solutions (Nu, Re) are nearly identical at vastly different values
of $\epsilon$, except for where there is a transition between the subsonic
and supersonic regimes.  We also see that Nu scales similarly in 2D and 3D,
and that Ma in 3D solutions appears to be a function of $\epsilon$ alone,
allowing for simple specification of the evolved Ma using input parameters.
The stratification of 
these polytropic atmospheres evolves in a complex
manner.  Future work should aim to 
understand the importance of stratification on
convective heat transport and other flow properties.

@@

\begin{acknowledgments}
EHA acknowledges the support of the University of Colorado's George 
Ellery Hale Graduate Student Fellowship.
This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
Computations were conducted 
with support by the NASA High End Computing (HEC) Program through the NASA 
Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades
with allocations GID s1647 and GID g26133.
We thank Jon Aurnou, Axel Brandenburg, Keith Julien, Mark Rast, and Jeff Oishi 
for many useful discussions. We also thank the three anonymous referees whose
careful comments greatly improved the quality of this letter.
\end{acknowledgments}

>>>>

%\documentclass[iop]{emulateapj}
\documentclass[aps, prfluids, onecolumn, notitlepage, nofootinbib, groupedaddress, amsfonts, amssymb, amsmath]{revtex4-1}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{natbib}
%\usepackage[colorlinks=True, linkcolor=blue, citecolor=blue]{hyperref}
%\usepackage[all]{hypcap}

@@

%%%%% Body of the paper
\section{Introduction}
\label{sec:intro}
Convection transports energy in stellar and planetary atmospheres
where flows are compressible and
feel the atmospheric stratification.  This stratification 
is significant in regions such as
the convective envelope of the Sun, which spans 14 density scale heights.
In the bulk of these systems, particularly in the deep interior,
flows are at very low Mach number (Ma).  Unfortunately,
numerical constraints have restricted most studies of 
compressible convection to high Ma.
These prior studies \cite{graham1975, chan&all1982,
hurlburt&all1984, cattaneo&all1990, brummell&all1996,
brandenburg&all2005} have provided insight into the nature of
convection in the low temperature,
high Ma region near the Sun's surface. Few fundamental
properties of low Ma compressible convection, such as the scaling of
convective heat transport, are known.

@@

Here we study the behavior of convective heat transport, 
quantified by the Nusselt number (Nu), in plane-parallel, 
two- and three-dimensional, polytropically stratified atmospheres.  
We vary $\epsilon$ and Ra while holding Pr, aspect ratio, boundary conditions,
and initial atmospheric stratification
constant.  We also examine the behavior of flow properties, as quantified by Ma and Re.
We find here that the scaling of Nu in stratified, compressible convection 
is similar to that in \RB convection,
and that this scaling is not appreciably changed by the magnitude of the superadiabaticity.

\section{Experiment} 
\label{sec:experiment}
We examine a monatomic ideal gas with an adiabatic index of
$\gamma = 5/3$ whose equation of state is $P = R\rho T$. This is consistent with the approach used in earlier work 
\cite{graham1975, chan&all1982, brandenburg&all2005,
hurlburt&all1984, cattaneo&all1990, cattaneo&all1991, brummell&all1996} 
and is the simplest stratified extension of RBC.
The atmospheres studied are initially polytropically stratified,
\begin{equation}
\begin{split}
\rho_0(z) &= \rho_{t}(1 + L_z - z)^m, \\
T_0(z)    &= T_{t}(1 + L_z - z),
\label{eqn:polytrope}
\end{split}
\end{equation}
where $m$ is the polytropic index and $L_z$ is the depth of the atmosphere.
The polytropic
index is set by the superadiabatic excess, $\epsilon = m_{ad} - m$, where
$m_{ad} = (\gamma - 1)^{-1}$ is the adiabatic value of $m$.
The height coordinate, $z$, increases upwards in the range $[0, L_z]$.
Subscript 0 indicates initial conditions and subscript $t$ indicates values
at $z = L_z$.   Stratified atmospheres have a fourth non-dimensional parameter,
the number of density scale heights, $n_{\rho} = \ln\left[\rho_0(z=0)/\rho_t\right]$.  We
specify the depth of the atmosphere, $L_z = e^{n_{\rho}/m} - 1$, by choosing
the initial value of $n_{\rho}$.
Throughout this work we set $n_{\rho} = 3$.    Satisfying hydrostatic
equilibrium sets the value of gravity, $g = RT_t (m + 1)$, which is
constant with depth.  We study atmospheres with aspect
ratios of 4 where both the $x$ and $y$ coordinates have the range $[0, 4L_z]$.
In our 2D cases, we only consider $x$ and $z$.

These domains are nondimensionalized by setting
$R = T_t = \rho_t = 1$ at $z = L_z$.
By this choice, the non-dimensional
length scale is the inverse temperature gradient scale and the 
timescale is the isothermal sound crossing time, 
$\tau_I$, of this unit length.
Meaningful convective dynamics occur on 
timescales of the atmospheric buoyancy time,
$t_b = \tau_I \sqrt{L_z m c_P/g\epsilon n_\rho}$.

At fixed $n_\rho$, convective dynamics are 
controlled by $\epsilon$ as well as the atmospheric diffusivities.
At a fixed value of
$\epsilon$, the diffusivities are set by the
Rayleigh number (Ra) and the Prandtl number (Pr),
\begin{equation}
\text{Ra}_{t} = \frac{g L_z^3 (\Delta S_0 / c_P)}{\nu_t\chi_t},
\qquad
\text{Pr} = \frac{\nu}{\chi},
\end{equation}
where $\Delta S_0 = \epsilon\ln (1 + L_z) = \epsilon n_\rho / m$ 
is the initial entropy difference across the domain,
$c_P = \gamma/(\gamma-1)$ is the specific heat at
constant pressure, $\nu$ is the thermal diffusivity, 
and $\chi$ is the kinematic viscosity.
Throughout this work we specify
that Pr $= 1$ and is depth invariant.
The initial thermal
conductivity, $\kappa_0 = \chi \rho_0$, is
constant with depth, such that (\ref{eqn:polytrope}) is in
thermal equilibrium ($\grad\cdot[\kappa_0\grad T_0] = 0$).
By these
choices, $\nu(z) \equiv \chi(z) \equiv \chi_t / \rho_0$.
This formulation 
sets Ra at the bottom of the domain greater than
Ra$_t$ by a factor of $e^{2n_\rho}$. Henceforth
when we specify Ra we are referring to Ra$_t$.  
The full values of $\kappa = \rho\chi$ and 
$\mu = \rho\nu$ (the dynamic viscosity) change as the density 
profile evolves.  
The diffusivities scale as
$\chi_t, \nu_t \propto \sqrt{g L_z^3 \epsilon / \text{Ra}_t}$.
Defining the thermal diffusion timescale as $t_\chi \equiv L_z^2 / \chi$, the
ratio of $t_\chi$ to the buoyancy time is
\begin{equation}
\frac{t_\chi}{t_b} = \left(\frac{c_P}{n_\rho}\right)^{1/2}\text{Ra}_t^{1/2}
\left(m_{ad} - \epsilon\right)^{1/2}.
\label{eqn:timescales}
\end{equation}
We carry out two experiments in this study. In the first,
we fix $\epsilon$ and increase Ra, thus increasing the ratio in
(\ref{eqn:timescales}). In the second, we fix Ra and vary $\epsilon$,
scaling the buoyancy time $t_b$ as $\epsilon^{-1/2}$
relative to the speed of sound; we see this reflected in the evolved Mach
number scaling (Fig. \ref{fig:ma_v_eps}). The ratio in (\ref{eqn:timescales}) is
independent of $\epsilon$ when $\epsilon \ll m_{ad}$.

The Fully Compressible Navier-Stokes equations,
\begin{align}
&\begin{aligned}
&\frac{\partial \ln\rho}{\partial t} + \grad\cdot\bm{u} 
    = -\bm{u}\cdot\grad\ln\rho,
	\label{eqn:continuity_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{\partial\bm{u}}{\partial t} + \grad T - 
&\nu\grad\cdot\lilstressT - \lilstressT\cdot\grad\nu =
-\bm{u}\cdot\grad\bm{u} - T\grad\ln\rho + \bm{g} + 
\nu\lilstressT\cdot\grad\ln\rho,
\label{eqn:momentum_eqn}
\end{aligned}\\
&\begin{aligned}
\frac{\partial T}{\partial t} -\frac{1}{c_V}\left(\right.\chi&\left.
    \grad^2 T + \grad T\cdot\grad\chi\right) =
	-\bm{u}\cdot\grad T - (\gamma-1)T\grad\cdot{\bm{u}}
	+ \frac{1}{c_V}\left(\chi\grad T \cdot\grad\ln\rho +
	\nu\left[\lilstressT\cdot\nabla\right]\cdot\bm{u}\right), 
	\label{eqn:energy_eqn}
\end{aligned}
\end{align}
are evolved with the viscous stress tensor given by
\begin{equation}
\sigma_{ij} \equiv \left(\frac{\partial u_i}{\partial x_j} + 
\frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\grad\cdot\bm{u}\right).
	\label{eqn:stress_tensor}
\end{equation}
Taking an inner product of
(\ref{eqn:momentum_eqn}) with $\rho\bm{u}$ and adding it to 
$\rho c_V\times$(\ref{eqn:energy_eqn}) reveals the full energy equation,
\begin{equation}
\frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{cond}}} = 0,
	\label{eqn:energy_eqn_full}
\end{equation}
where
$
\bm{F}_{\text{conv}} \equiv \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}}
$
is the convective flux and $\bm{F}_{\text{cond}} = -\kappa \grad T$
is the conductive flux.
The individual contributions to $\bm{F}_{\text{conv}}$ are the enthalpy flux, 
$\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$;
the kinetic energy flux, 
$\bm{F}_{\text{KE}} \equiv \rho|\bm{u}|^2\bm{u}/2$;
the potential energy flux,
$\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ (with $\phi \equiv -gz$);
and the viscous flux, 
$\bm{F}_{\text{visc}} \equiv -\rho\nu\bm{u}\cdot\lilstressT$.
Understanding how each of these fluxes interact  
is crucial in characterizing convective heat transport.

@@

\section{Results \& Discussion}
\label{sec:results}

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/ma_v_Ra.png}
\caption{The mean adiabatic Mach number of long-time-averaged profiles
is shown.  Error bars show the full range of Ma over the depth of the
atmosphere.
(a) Ma, at various values of Ra, 
is plotted as a function of $\epsilon$.
(b) Ma, at various values of $\epsilon$, 
is plotted as a function of Ra/Ra$_{\text{crit}}$.
Larger symbols with white dots designate 3D runs.
\label{fig:ma_v_eps} }
\end{figure}

@@

\subsection{Fluid Numbers \& Flows}

@@

\begin{figure}[t!]
\includegraphics[width=\textwidth]{./figs/snapshots_fig.png}
\caption{Characteristic entropy fluctuations in evolved 2D flows roughly
140$t_b$ after the start of simulations. 
The time- and horizontally-averaged profile is removed in all cases.  
(a) A low Ma flow at moderate Ra. (b) A high Ma flow at the same Ra as in (a).
(c) A high Ma flow at high Ra.  In all cases, the broad upflow and narrow downflows
traditionally seen in stratified convection are apparent.
Shock systems can be seen in the upper atmosphere of the high Ma flows,
for example at $(x, z) \sim (70, 15-19)$ in (b) and $(x, z) \sim 
(65, 17-19)$ in (c).
\label{fig:entropy_snapshots} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/re_and_nu_v_Ra.png}
\caption{
Flow properties at high and low $\epsilon$. 
(a) Nu vs. Ra/Ra$_{\text{crit}}$.
Errors bars indicate the variance of Nu with depth;
large error bars indicate a poorly converged solution.
(b) Re vs. Ra/Ra$_{\text{crit}}$.
Re is measured at the midplane of the atmosphere.
Larger symbols with white dots designate 3D runs.
 \label{fig:re_and_nu_v_ra}
}
\end{figure}

@@

The variation of Nu with Ra is shown in 
Fig. \ref{fig:re_and_nu_v_ra}a.  We find that the Nu depends primarily
on Ra, not on $\epsilon$, except where dynamical regimes change.
In 2D and at low to moderate Ra, 
Nu $\appropto$ Ra$^{1/3}$ regardless of $\epsilon$,
reminiscent of scaling laws in \RB boundary layer theory 
\cite{grossman&lohse2000, ahlers&all2009, king&all2012}.
As the flow becomes supersonic,  Nu $\appropto$ Ra$^{1/5}$.
It is also important to note that, in 2D,
the value of Nu is heavily dependent upon the specific thermodynamic
structures of the solution, and slight changes in
Ra can result in a simulation converging to one solution or another. 
Select simulations were run at higher aspect ratios (8 and 16), and similar flow
morphologies were obtained, suggesting that these states are not highly
sensitive to aspect ratio.
In our limited 3D runs, it appears that Nu $\appropto$ Ra$^{2/7}$, a classic scaling law
seen in RBC \cite{johnston&doering2009}.

@@

\subsection{Change of Stratification}

\begin{figure}[t]
\includegraphics[width=0.5\textwidth]{./figs/density_v_ra.png}
\caption{\label{fig:nrho_v_ra} 
Solid symbols show the density contrast measured
in density scale heights between the upper and lower boundary, 
$n_\rho = \ln[\rho(z=0)/\rho(z=L_z)]$.
Empty symbols show 
$n_\rho = \ln[\text{max}(\rho)/\text{min}(\rho)]$. 
At low $\epsilon$ the evolved
$n_{\rho}$ is close to the initial conditions of $n_\rho = 3$.  
At high $\epsilon$,
the density stratification decreases.  Once the mean 
Ma approaches 1 (at Ra/Ra$_{\text{crit}} \approx \{10^2, 10^3\}$ for $\epsilon = \{1, 0.5\}$
as in Fig. \ref{fig:ma_v_eps}b), density inversions form within the thermal
boundary layers. Larger symbols represent 3D runs.}
\end{figure}

@@

\section{Discussion \& Future Work}
In summary, we have found that the evolved flow properties of stratified,
compressible convection scale in a manner reminiscent of RBC.
We argue that polytropically stratified atmospheres are the natural
extension of the RBC problem with an additional control parameter, $\epsilon$,
whose primary role is to set the Ma of the flows.  We show that other properties
of the evolved solutions (Nu, Re) are nearly identical at vastly different values
of $\epsilon$, except for where there is a transition between the subsonic
and supersonic regimes.  We also see that Nu scales similarly in 2D and 3D,
and that Ma in 3D solutions appears to be a function of $\epsilon$ alone,
allowing for simple specification of the evolved Ma using input parameters.
The stratification of 
these polytropic atmospheres evolves in a complex
manner.  Future work should aim to 
understand the importance of stratification on
convective heat transport and other flow properties.

@@

\begin{acknowledgments}
EHA acknowledges the support of the University of Colorado's George 
Ellery Hale Graduate Student Fellowship.
This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
Computations were conducted 
with support by the NASA High End Computing (HEC) Program through the NASA 
Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades
with allocations GID s1647 and GID g26133.
We thank Jon Aurnou, Axel Brandenburg, Keith Julien, Mark Rast, and Jeff Oishi 
for many useful discussions. We also thank the three anonymous referees whose
careful comments greatly improved the quality of this paper.
\end{acknowledgments}
